---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# rtweettree

<!-- badges: start -->
<!-- badges: end -->

The goal of rtweettree is to recursively scrape a twitter tweet and all replies, quotes and likes (that the API provides) and visualize them in a network graph. The functionalities to scrape twitter data are heavily based on the excellent [**{{rtweet}}**](https://github.com/ropensci/rtweet) package. The graph network manipulation functionalities rely on the amazing [**{{tidygraph}}**](https://github.com/thomasp85/tidygraph) package and visualized with [**{{ggraph}}**](https://github.com/thomasp85/ggraph).

## Responsible use

**{{rtweettree}}** should be used in strict accordance with Twitter's [developer terms](https://developer.twitter.com/en/developer-terms/more-on-restricted-use-cases).

## Installation

To get the current development version from Github:

```{r eval=FALSE}
## install remotes package if it's not already
if (!requireNamespace("remotes", quietly = TRUE)) {
  install.packages("remotes")
}

## install dev version of rtweettree from github
remotes::install_github("UrsWilke/rtweettree")
```

## load rtweettree package
```{r load}
library(rtweettree)
```

## Usage

In order to use **{{rtweettree}}** please refer to [the according section of **{{rtweet}}**](https://github.com/ropensci/rtweet#usage). It is probably good advice to first feel comfortable with [**{{rtweet}}**](https://github.com/ropensci/rtweet).

An example how to create a subtweet network graph from a tweet status_id is shown in the [vignette for tree visualization](articles/visualize_tree.html). In this link, I didn't manage to render the interactive ggiraph correctly yet, but after installing rtweettree it can be seen in the vignette:

<!-- TODO: repair website and rendering -->

```{r tree_viz, eval=FALSE}
vignette("visualize_tree", package = "rtweettree")
```

