---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# rtweettree

<!-- badges: start -->
<!-- badges: end -->

The goal of rtweettree is to scrape a twitter tweet and all replies, quotes and likes (recursively) and visualize them in a network graph.

## Responsible use

**{{rtweettree}}** should be used in strict accordance with Twitter's [developer terms](https://developer.twitter.com/en/developer-terms/more-on-restricted-use-cases).

## Installation

To get the current development version from Github:

```{r}
## install remotes package if it's not already
if (!requireNamespace("remotes", quietly = TRUE)) {
  install.packages("remotes")
}

## install dev version of rtweettree from github
# remotes::install_github("UrsWilke/rtweettree")
```

## load rtweettree package
```{r load}
library(rtweettree)
```

## Usage

In order to use **{{rtweettree}}** please refer to [the according section of **{{rtweet}}**](https://github.com/ropensci/rtweet#usage).

An example how to create a subtweet network graph is shown in the [vignette for tree visualization](https://github.com/urswilke/rtweettree/blob/master/vignettes/visualize_tree.Rmd)

```{r tree_viz}
vignette("visualize_tree", package = "rtweettree")
```

