---
title: "Getting started"
output: 
  rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE, eval=TRUE}
knitr::opts_chunk$set(
  # eval=TRUE,
  eval=FALSE,
  # echo=TRUE,
  collapse = TRUE,
  # cache = TRUE,
  comment = "#>"
)
```

This vignette shows how {rtweettree} can be used to generate network graphs
visualizing the reactions on a tweet (replies, quotes and favorites) as a tree.
The nodes correspond to tweets and the users who interact with them with these
reactions.


## Load packages

The following libraries are loaded:

```{r libs, eval = TRUE, message=FALSE}
library(dplyr)
library(rtweettree)
library(ggraph)
library(tidygraph)
library(ggiraph)
```

## Scraping 

**rtweettree** tries to scrape as much as information as possible that might be
related to the tweet at the root of the tree. Please beware that the twitter API
doesn't allow to scrape all sub tweets. And that for large amounts of
interactions to a tweet it can take a long time due to rate limits (please refer
to [the twitter developer website on rate
limits](https://developer.twitter.com/en/docs/basics/rate-limiting), or the
[documentation of the rtweet
functions](https://docs.ropensci.org/rtweet/reference/index.html)).

### Scrape tweets

Tweets on twitter are uniquely classified via the status id:

```{r status_id}
# Replace this number by any status_id (the last number in the twitter.com url of a tweet):
main_status_id <- "1438481824922181635"
```

Now let's scrape:

```{r scrape}
rtweettree_data_scraped <- rtweettree_data(main_status_id)
```

```{r save_example_data, include=FALSE}
rtweettree_data_example <- rtweettree_data_scraped
usethis::use_data(rtweettree_data_example, overwrite = TRUE)
```


To allow to test the package in offline use (and without setting up an account
for the twitter api), you can also load this dataset which is already included in the package:
```{r load_example_data, eval=TRUE}
rtweettree_data_scraped <- rtweettree_data_example
```



## Create tbl_graph object

The relevant twitter information of these tweets is translated into a tidygraph network object: 

```{r tbl_graph, eval=TRUE, message=FALSE}
g <- rtweettree_tbl_graph(rtweettree_data_scraped)
```


```{r tbl_graph2, eval=TRUE}
g
```

Now we can make use of the full power of tidygraph, e.g.,  add a column to the
nodes tibble, showing how far the respective node is from the main tweet in the
graph:

```{r data_manip, eval=TRUE}
g <- g %>%     
  # calculate the distance to the tree root with tidygraph:
  mutate(dist_to_root = node_distance_from(node_is_source()))
g %>% as_tibble()
```


## Visualize graphs

Please make sure not to publish information from Twitter you are not allowed to
and to comply in strict accordance with the [twitter developer
terms](https://developer.twitter.com/en/developer-terms/more-on-restricted-use-cases)!
The example rtweet data in this article only contains the tweets of three dummy
accounts I created. But probably you're not allowed to publish all this
information for the `main_status_id` of any other tweet.

The generated graph object consists of nodes representing tweets and users.
These are connected by edges that can be

* replies & quotes (connecting tweets),
* "by" connecting the author to his respective tweet, and 
* "like"/"retweet" connecting the user to the tweet he liked/retweeted. 

### Hierarchical tree plot with ggraph

We can generate a simple tree graph of the various tweets and users with:

```{r simpleplot, eval=TRUE, fig.width=6, fig.height=5}
g %>% 
  ggraph() + 
  geom_node_point(aes(color = dist_to_root), size = 3) + 
  geom_edge_diagonal(aes(color = type))
```

This yields something similar to the autoplot() method of the package:

```{r ggraph2, eval=TRUE, fig.width=6, fig.height=5}
# (In order to include the profile pictures in the graph you need an internet
# connection)
g1 <- ggplot2::autoplot(g, add_profile_pics = TRUE)
g1
```


### Using ggiraph

With ggiraph we can generate an interactive tree graph:


```{r ggiraph, eval=TRUE, results='asis'}
# Add on click information to the graph nodes:
g1$data$onclick  <- glue::glue('window.open("{g1$data$url}")')

# Reproduce the above ggraph using the according ggiraph components:
g2 <- g1 +
  geom_edge_diagonal(aes(color= type)) +
  # This adds rectangles around users and tweets:
  ggforce::geom_mark_rect(aes(
    x = g1$data$x,
    y = g1$data$y,
    color = g1$data$type)
  ) +
  # We have to replace the color scale, because this time it's discrete and not
  # continuous:
  scale_color_discrete(name = "type") +
  geom_point_interactive(aes(
    x=g1$data$x,
    y = g1$data$y,
    color = type,
    data_id = g1$data$screen_name,
    tooltip = g1$data$label,
    onclick = g1$data$onclick),
    size = 3
  ) +
  ggtitle(
    "Hover over the nodes to see the tweets/user names.", 
    subtitle = "Click on the nodes to open the tweets/users on twitter.com"
  )
p <- girafe(code = print(g2), width_svg = 6, height_svg = 5)

p <- girafe_options(x = p,
                    opts_zoom(min = 0.3, max = 5),
                    opts_hover(girafe_css(css = "stroke:yellow;",
                                          point = "stroke-width:6px")))

p
```

### Customizing `autoplot()`

We can also customize the ggraph object by passing arguments to the autoplot methods, e.g. by 

* not including the profile pictures (`add_profile_pics = FALSE`)
* or using another [layout](https://ggraph.data-imaginist.com/articles/Layouts.html) 

```{r, eval=TRUE, message=FALSE}
ggplot2::autoplot(rtweettree_data_scraped, add_profile_pics = FALSE, layout = "stress")
```

