---
title: "Visualize tweet tree"
output: 
  rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{scrape_tree}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE, eval=TRUE}
knitr::opts_chunk$set(
  # eval=TRUE,
  eval=FALSE,
  # echo=TRUE,
  collapse = TRUE,
  # cache = TRUE,
  comment = "#>"
)

pic_path <- "visualize_tree_files"
```

## Load packages

```{r libs, eval = TRUE, message=FALSE}
library(dplyr)
library(rtweettree)
library(ggraph)
library(tidygraph)
```

## Scraping 

Unfortunately, the twitter API (rtweet is based on) doesn't allow to scrape all sub tweets. 
For small amounts of replies/quotes/likes this often results in no subtweets at all.
On the other hand, for large amounts it can take a long time due to rate limits (please refer to [the twitter developer website on rate limits](https://developer.twitter.com/en/docs/basics/rate-limiting), or the [documentation of the rtweet functions](https://docs.ropensci.org/rtweet/reference/index.html)).

### Scrape tweets

```{r status_id, cache=TRUE}
# Replace this number by any status_id (the last number in the twitter.com url of a tweet):
main_status_id <- "1289565453707173889"
```


```{r scrape, cache=TRUE}
df_main_status <- rtweet::lookup_statuses(main_status_id)
# Scrape available subtweets:
df_tree <- search_tree(main_status_id)
```

### Scrape timelines

```{r scrape_timelines, cache=TRUE}
tree_ids <- df_tree$user_id %>% unique()
# Scrape the timelines of the users scraped:
df_tls <- scrape_timelines(tree_ids)
```

### Scrape likes

```{r scrape_favs, cache=TRUE}
df0 <- df_main_status %>%
  dplyr::filter(status_id == main_status_id) %>%
  dplyr::select(to = status_id, user_id) %>%
  dplyr::mutate(from = "root", type = "root")
tweet_edges <-
  find_connections_rec(dplyr::bind_rows(df_tree, df_tls), df0)
ids <- tweet_edges$user_id %>% unique()
# Scrape the likes of the users scraped:
df_favs <- scrape_favs2(ids, main_status_id)
```

## Create tbl_graph object

```{r tbl_graph, cache=TRUE}
g <- 
  create_tweet_tbl_graph(df_main_status, df_tree, df_tls, df_favs) %>% 
  mutate_at(c("screen_name", "label"),  ~(factor(.)) %>% as.numeric()) %E>% 
  mutate_at(c("screen_name"),  ~(factor(.)) %>% as.numeric())  
usethis::use_data(g, overwrite = TRUE, internal = TRUE)
```

```{r save_g}
# saveRDS(g, paste0(here::here(), "/vignettes/visualize_tree_files/tbl_graph.RDS"))
```


```{r load_g_ALT, eval=TRUE}
# g <- readRDS(paste0(here::here(), "/vignettes/visualize_tree_files/tbl_graph.RDS"))
```



## Visualize graphs

```{r load_g, eval=TRUE, include=FALSE}
# load g from internal dataset
g <- rtweettree:::g
```

### Using ggraph

Circlepack plot:



```{r ggraph_circlepack, eval=TRUE}

p <- g %>%
  ggraph('circlepack', circular = T) +
  geom_node_circle(aes(fill = dist_to_center), n = 50) +
  scale_fill_viridis_c(direction = -1) +
  coord_fixed()
p
```


```{r ggraph_circlepack_str, eval=TRUE, include=FALSE}
fig_name <- "ggraph_circlepack.png"
fig_path_name <- paste0(pic_path, "/", fig_name)
```


```{r ggraph_circlepack_save, include=FALSE}
ggsave(fig_name, p, path = pic_path)
```


```{r ggraph_circlepack_pic, include=FALSE, eval = TRUE}
knitr::include_graphics(fig_path_name)
```


Hierarchical tree plot:

```{r ggraph, eval=TRUE}
g1 <- g %>% ggraph()

# Hack to put all user nodes on the bottom line of the graph:
g1$data$y[g1$data$type == "user"] <- min(g1$data$y)
g1 +
  geom_edge_diagonal(aes(color= type)) +
  geom_node_point(aes(color = dist_to_center,
                      shape = type))
```

```{r gghier_str, eval=TRUE, include=FALSE}
fig_name <- "gghier.png"
fig_path_name <- paste0(pic_path, "/", fig_name)
```


```{r gghier_save, include=FALSE}
ggsave(fig_name, p, path = pic_path)
```


```{r gghier_pic, include=FALSE, eval = TRUE}
knitr::include_graphics(fig_path_name)
```

### Using ggiraph (for interactivity)

* Hover over the nodes to see the tweets/users. (in order to comply to the twitter terms of use this information will be anonymized for this public vignette; see below)
* Click on the nodes to open the tweets/users on twitter.com

```{r ggiraph, eval=TRUE}
# Add on click information to the graph nodes:
g1$data$onclick  <- glue::glue('window.open("{g1$data$url}")')

# anonymize hover information, as it is not allowed to publish this:
g1$data$label <- sample(LETTERS, length(g1$data$label))

# Reproduce the above ggraph using the according ggiraph components:
g2 <- g1 +
  geom_edge_diagonal(aes(color= type)) +
  ggforce::geom_mark_rect(aes(x = g1$data$x,
                              y = g1$data$y,
                              # filter = type == 'user',
                              color = g1$data$type)
  ) +
  ggiraph::geom_point_interactive(aes(x=g1$data$x,
                                      y = g1$data$y,
                                      color = type,
                                      data_id = g1$data$screen_name,
                                      tooltip = g1$data$label,
                                      onclick = g1$data$onclick),
                                  size = 3)
p <- ggiraph::girafe(ggobj = g2,
                options = list(
                  ggiraph::opts_zoom(min = 0.3, max = 5),
                  ggiraph::opts_hover(ggiraph::girafe_css(css = "stroke:yellow;",
                                                          point = "stroke-width:6px"))
                )
)

p
```

```{r ggiraph_str, eval=TRUE, include=FALSE}
fig_name <- "ggiraph.html"
fig_path_name <- paste0(pic_path, "/", fig_name)
```


```{r ggiraph_save, include=FALSE}

withr::with_dir(pic_path, htmlwidgets::saveWidget(p, file = fig_name)) 
# htmlwidgets::saveWidget(p, file = fig_name)
```


```{r ggiraph_pic, echo=FALSE, eval = TRUE}
# withr::with_dir(pic_path, htmlwidgets::saveWidget(p, file = fig_name)) 
# htmltools::tags$iframe(title = "My embedded document", src = fig_name)
# htmltools::includeHTML(fig_path_name)
# knitr::include_graphics(fig_path_name)
```


